Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-26 paper/paper.Rmd
link back to example in intro, add examples

# Introduction

@@

Most often multiple spatial partitioning methods can be used for a dataset.
It is recommended (required) to make oneself familiar with the available methods and to decide on one based on the specific characteristics of the dataset at hand and the prediction purpose of the fitted model.
The prediction purpose is the model's ability for which areas or zones it actually can make predictions.
For example, ...
<!--JM: maybe refer back to the crop example of the intro to make the point better comprehensible than just giving the mere theory-->

@@

- Do natural groupings exists in the data? <!--Example-->
- How dense are the observations scattered both in space and time?
The closer observations are in space and/or time, the more similar they are, and hence the greater is the effect of spatio-temporal autocorrelation.
- Are some of the predictor variables under consideration known to be highly affected by spatiotemporal autocorrelation such as ... <!-- pls add an example -->?

>>>>

# Introduction {#sec:intro}

@@

Most often multiple spatial partitioning methods can be used for a dataset.
It is recommended (required) to make oneself familiar with the available methods and to decide on one based on the specific characteristics of the dataset at hand and the prediction purpose of the fitted model.
The prediction purpose is the model's ability for which areas or zones it actually can make predictions.
In the crop example given in section \@ref(sec:intro) this would be to distinguish and predict different crop types. 
Hence, the CV partitioning is done on the crop level to receive a honest estimate of the model's performance.

@@

- Do natural groupings exists in the data? Examples include agricultural fields, forest stands, lithology types, etc.
- How dense are the observations scattered both in space and time?
  The closer observations are in space and/or time, the more similar they are, and hence the greater is the effect of spatio-temporal autocorrelation.
- Are some of the predictor variables under consideration known to be highly affected by spatiotemporal autocorrelation such as temperature or precipitation?
